---
title: "Perenniality (and/or) management drives soil biological communities and functions"
author: "Christine D. Sprunger, Ariane L. Peralta, Steven Culman, Jay T. Lennon, Sieglinde S. Snapp"
date: "Last updated on `r format(Sys.time(), '%d %B, %Y')`"
header-includes:
  - \usepackage{array}
  - \usepackage{graphics}
  - \usepackage[utf8]{inputenc}
output: 
  pdf_document:
  fig_caption: true
---

Project Description: Fill out

# Initial Setup
```{r Initial Setup, include=FALSE}
rm(list=ls())
setwd("~/GitHub/PWES_SoilBio/analyses")
se <- function(x, ...){sd(x, na.rm = TRUE)/sqrt(length(na.omit(x)))}
ci <- function(x, ...){1.96 * sd(x,na.rm = TRUE)}

# Code Dependencies
source("../bin/DiversityFunctions.R")
source("../bin/MothurTools.R")
require("vegan")
require("nlme")
require("reshape")
require("ggplot2")
require("ade4")
require("png")
require ("agricolae")
require("tidyr")
require("reshape2")
require("picante")
```
#Import Files
## Environmental Data
```{r Import Files - Env}
# Import Environmental Data
design <- read.csv("../data/PWES_KBS_design.csv", header=TRUE)
soil <- read.csv("../data/PWES_KBS_soil.csv", header=TRUE)
```

## Nematode Data
```{r Import Files - Nema}
# Import Environmental Data
nema <- read.csv("../data/PWES_nema.csv", header=TRUE)
nema <- na.omit(nema)
dim(nema)
nema.design <- nema[,c(1:9)]
nema.comm <- nema[,-c(1:9)]
dim(nema.comm)

# Remove taxa with less than one occurences across all sites
#nema.comm.a <- nema.comm[, which(colSums(nema.comm) >= 1)]
#dim(nema.comm.a)

# Make Relative Abundance Matrices removed xxx_sample = NA
dataRELnema <- nema.comm
for(i in 1:dim(nema.comm)[1]){
  dataRELnema[i,] <- nema.comm[i,]/sum(nema.comm[i,])
}

dim(dataRELnema)

nemaREL <- cbind(nema.design,dataRELnema)
dim(nemaREL)
```

## Microbial Data
```{r Import Files - Bacteria, include=FALSE}
# Import OTU data
# Import Raw Data
otu.in <- read.otu("../data/PWES.bac.final.shared")

# Correct Sample IDs and Subset Original Design File
rownames(design) <- gsub("^micro-", "PWESmicro_", design$Micro_ID)
design.otu <- design[which(rownames(design) %in% rownames(otu.in)), ]
otu <- otu.in[which(rownames(otu.in) %in% rownames(design.otu)), ]
otu <- otu[match(row.names(design.otu), row.names(otu)), ]
all.equal(rownames(otu), rownames(design.otu))

# Remove OTUs with less than two occurences across all sites
otus <- otu[, which(colSums(otu) >= 2)]

# Make Presence Absence Matrix
dataPA <- (otus > 0) * 1

# Make Relative Abundance Matrices
dataREL <- otus
for(i in 1:dim(otus)[1]){
  dataREL[i,] <- otus[i,]/sum(otus[i,])
}

# Import Taxonomy File
otu.tax <- read.tax(taxonomy = "../data/PWES.bac.final.0.03.taxonomy",
                   format = "rdp", tax.levels = 6, col.tax = 3)
```
# Diversity Metrics - Hypothesis Testing
```{r Diversity Metrics - Bacteria}
# Rarefy Abundances (min abundance is 88033. We are sampling to 80000)
min(rowSums(otus))
PWESdata.r <- rrarefy(otus, 80000)

# Fisher's Alpha
fisher <- fisher.alpha(PWESdata.r)

# Species Richness
richness <- rowSums((PWESdata.r >= 1))

# Shannon Diversity
shannon <- diversity(PWESdata.r, "shannon")

# Simpson's Evenness
simp.even <- apply(PWESdata.r, 1, simp_even)

#Pielou’s evenness
J <- shannon/log(specnumber(PWESdata.r[,-c(1:1)]))

#combined richness, diversity, evenness
diversity <- cbind(design,richness,shannon,simp.even,J)
```

# Diversity Metrics - Hypothesis Testing
```{r Hypothesis Testing - Bacteria}
# First check the order
length(design$Management) == length(fisher)
all.equal(gsub("-", "", rownames(design)), names(fisher))
library(lme4)

richness.lm <- lme(richness ~ Date*Management*Plant, random = ~1|Block, data = diversity)
plot(richness.lm)
richness.lm
anova(richness.lm)

evenness.lm <- lme(simp.even ~ Date*Management*Plant, random = ~1|Block, data = diversity)
plot(evenness.lm)
evenness.lm
anova(evenness.lm)

shannon.lm <- lme(shannon ~ Date*Management*Plant, random = ~1|Block, data = diversity)
plot(shannon.lm)
shannon.lm
anova(shannon.lm)

#calculate mean and se
library(reshape2)
library(dplyr)

diversity.1 <- subset(diversity, Year == 2013)
dim(diversity.1)

summary <- diversity.1 %>% group_by(Management, Plant) %>% summarise(mean.richness=mean(richness), se.richness=se(richness), mean.shannon=mean(shannon), se.shannon=se(shannon))
print(summary)

```

#Plot shannon diversity 
```{r Plot - Shannon Diversity}
date_1 <- as.factor(diversity$Date)
labels <- c("Jun-11"="2011","Jun-12"="2012", "Jun-13"="2013")

# Graphing Shannon Diversity - Date x Plant over Mgmt
p <- ggplot(diversity, aes(x=Date, y=shannon, color=as.factor(Plant)))+ scale_color_manual(name="Plant", values=c("#D55E00", "#0072B2"), labels = c("Annual", "Perennial")) + stat_summary(fun.data=mean_cl_boot,size=0.75) 
p1=p+geom_smooth(method="lm")+facet_wrap(~Management)+facet_grid(. ~ Management)
p1 + theme_bw() + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line 
          =element_line(colour = "black")) + 
    theme(axis.title=element_text(vjust=1,size=14,face="bold"),
          axis.text=element_text(size=14), axis.text.x = element_text(vjust=0.65, hjust=0.5, 
          size=14), panel.border = element_rect(colour = "black",size=1)) + 
    theme(axis.ticks.length=unit(0.3,"cm")) + labs(x = "Year", y = "Shannon Diversity Index (H')") + 
    theme(strip.text.x = element_text(size=14, face="bold"), strip.text.y =   
          element_text(size=14, face="bold"), strip.background = element_rect(colour="black",
          fill="white", size=1)) +
    scale_x_discrete(breaks=c("Jun-11", "Jun-12", "Jun-13"), labels=c("2011", "2012", 
          "2013"))
  
ggsave("../figures/shannon.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=300, limitsize=TRUE)
```
# Simple Hypothesis Testing - Microbes
```{r perMANOVA - Bacteria}
#PERMANOVA Date|Plant|Management
new.data <-cbind(design,dataREL)
adonis = adonis(new.data[,-c(1:9)]~Block+Date*Management*Plant, method = "bray", data = new.data, perm=1000)
adonis
```
# Microbial Ordinations

## Principal Coordinates Ordination
```{r Ordination (PCoA) - Bacteria - all years}
# Principal Coordinates Analysis
dataREL.dist <- vegdist(dataREL, method="bray")

pcoa <- cmdscale(dataREL.dist, k=3, eig=TRUE, add=FALSE)
  # Classical (Metric) Multidimensional Scaling; returns PCoA coordinates
  # eig=TRUE returns eigenvalues; k = # of dimensions to calculate

explainvar1b <- round(pcoa$eig[1] / sum(pcoa$eig), 3) * 100
explainvar2b <- round(pcoa$eig[2] / sum(pcoa$eig), 3) * 100
sum.eigb <- sum(explainvar1b, explainvar2b)

explainvar1b #23.1
explainvar2b #9.1
```

```{r}
# Principal Coordinates Analysis Mgmt*Date
all.equal(rownames(design), rownames(dataREL))
pcoa.groups <- paste(new.data$Management, new.data$Date, sep = "_")
pcoa.points <- data.frame(pcoa$points, group = pcoa.groups)

# Calculate Centroids (mean and SE)
pcoa.L.centroids <- melt(pcoa.points, id="group", measure.vars = c("X1", "X2"))
pcoa.centroids <- acast(pcoa.L.centroids, variable ~ group, mean)
pcoa.centroids.se <- acast(pcoa.L.centroids, variable ~ group, se)
pcoa.centroids.sd <- acast(pcoa.L.centroids, variable ~ group, sd)

# Combine
pcoa.cent.dataframe <- cbind(t(pcoa.centroids), t(pcoa.centroids.se))
colnames(pcoa.cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
pcoa.cent.treats <- rownames(pcoa.cent.dataframe)

pcoa.col <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 2)) # Management
pcoa.shape <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 1))  # Date

# Principal Coordinates Analysis (Mgmt*Date)
df1a <- as.data.frame(pcoa.cent.dataframe)
plot1a <- ggplot(df1a, aes(x=V1, y=V2, colour=pcoa.col, shape = pcoa.shape,
                 group = interaction(pcoa.col, pcoa.shape))) + theme_bw() 
plot1a + theme(panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(), 
               axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") + 
  geom_point(aes(fill=pcoa.col), colour = "black", size=6, stroke = 0.75) + 
  scale_colour_manual(labels = c("2011","2012", "2013"), 
                      values = c("#FFFFFF", "#FFFF00","#336600")) + 
  scale_fill_manual(labels = c("2011","2012", "2013"), 
                    values = c("#FFFFFF", "#FFFF00","#336600"))  + 
  scale_shape_manual(labels = c("HighN","LowN","Organic"),
                     values = c(21, 24, 22)) +
  #coord_cartesian(xlim = c(-0.25, 0.5), ylim = c(-0.35, 0.3)) + 
  theme(axis.title = element_text(size=18), axis.text=element_text(size=14), 
          axis.text.x = element_text(size=14), 
          panel.border = element_rect(colour = "black", size=1.25)) + 
  theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("PCoA 1 (23.1%)") + ylab("PCoA 2 (9.1%)") + 
  labs(fill = "Date", shape = "Management") +
  guides(fill = guide_legend(override.aes = list(pch=21, size = 4, colour="black")),
         shape = guide_legend(override.aes = list(size = 4, fill="black")))  + 
         annotate("text", x = -0.11, y = 0.12, label = "bacteria")

ggsave("../figures/16SrRNA_PWES_YrMgmt.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)

```

```{r}
# Principal Coordinates Analysis (Mgmt*Plant)
all.equal(rownames(design), rownames(dataREL))
pcoa.groups <- paste(new.data$Management, new.data$Plant, sep = "_")
pcoa.points <- data.frame(pcoa$points, group = pcoa.groups)

# Calculate Centroids (mean and SE)
pcoa.L.centroids <- melt(pcoa.points, id="group", measure.vars = c("X1", "X2"))
pcoa.centroids <- acast(pcoa.L.centroids, variable ~ group, mean)
pcoa.centroids.se <- acast(pcoa.L.centroids, variable ~ group, se)
pcoa.centroids.sd <- acast(pcoa.L.centroids, variable ~ group, sd)

# Combine
pcoa.cent.dataframe <- cbind(t(pcoa.centroids), t(pcoa.centroids.se))
colnames(pcoa.cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
pcoa.cent.treats <- rownames(pcoa.cent.dataframe)

pcoa.col <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 2)) # Management
pcoa.shape <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 1))  # Plant

#Plot
df2a <- as.data.frame(pcoa.cent.dataframe)
plot2a <- ggplot(df2a, aes(x=V1, y=V2, colour=pcoa.col, shape = pcoa.shape,
                 group = interaction(pcoa.col, pcoa.shape))) + theme_bw() 
plot2a + theme(panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(), 
               axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") + 
  geom_point(aes(fill=pcoa.col), colour = "black", size=6, stroke = 0.75) + 
  scale_colour_manual(labels = c("Annual","Perennial"), 
                      values = c("#D55E00", "#0072B2")) + 
  scale_fill_manual(labels = c("Annual","Perennial"), 
                    values = c("#D55E00", "#0072B2")) + 
  scale_shape_manual(labels = c("HighN","LowN","Organic"),
                     values = c(21, 24, 22)) +
  #coord_cartesian(xlim = c(-0.25, 0.5), ylim = c(-0.35, 0.3)) + 
  theme(axis.title = element_text(size=18), axis.text=element_text(size=14), 
          axis.text.x = element_text(size=14), 
          panel.border = element_rect(colour = "black", size=1.25)) + 
  theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("PCoA 1 (23.1%)") + ylab("PCoA 2 (9.1%)") + 
  labs(fill = "Plant", shape = "Management") +
  guides(fill = guide_legend(override.aes = list(pch=21, size = 4, colour="black")),
         shape = guide_legend(override.aes = list(size = 4, fill="black"))) + 
         annotate("text", x = -0.11, y = 0.12, label = "bacteria-all years")

ggsave("../figures/16SrRNA_PWES_PlantMgmt.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)

```

## Principal Coordinates Ordination -BACTERIA seaparate years
```{r Ordination (PCoA.2011) - Bacteria}
new.data <-cbind(design,dataREL)
# PERMANOVA - 2011 only
new.data.2011 <- subset(new.data, Year == 2011)
adonis.2011 = adonis(new.data.2011[,-c(1:9)] ~Block+Management*Plant, method = "bray", data = new.data.2011, perm=1000)
adonis.2011

dataREL.dist <- vegdist(new.data.2011[,-c(1:9)], method="bray")

pcoa <- cmdscale(dataREL.dist, k=3, eig=TRUE, add=FALSE)
  # Classical (Metric) Multidimensional Scaling; returns PCoA coordinates
  # eig=TRUE returns eigenvalues; k = # of dimensions to calculate

explainvar1b <- round(pcoa$eig[1] / sum(pcoa$eig), 3) * 100
explainvar2b <- round(pcoa$eig[2] / sum(pcoa$eig), 3) * 100
sum.eigb <- sum(explainvar1b, explainvar2b)

explainvar1b #35.7
explainvar2b #8.9

# Added by Mario ######
soil2011 <- soil[soil$Year == 2011, 17:22]
fit <- envfit(pcoa,soil2011,perm=1000)
fit.coords <- as.data.frame(fit$vectors$arrows) * 0.1
############

# Principal Coordinates Analysis (Mgmt*Plant) - 2011 only
pcoa.groups <- paste(new.data.2011$Management, new.data.2011$Plant, sep = "_")
pcoa.points <- data.frame(pcoa$points, group = pcoa.groups)

# Calculate Centroids (mean and SE)
pcoa.L.centroids <- melt(pcoa.points, id="group", measure.vars = c("X1", "X2"))
pcoa.centroids <- acast(pcoa.L.centroids, variable ~ group, mean)
pcoa.centroids.se <- acast(pcoa.L.centroids, variable ~ group, se)
pcoa.centroids.sd <- acast(pcoa.L.centroids, variable ~ group, sd)

# Combine
pcoa.cent.dataframe <- cbind(t(pcoa.centroids), t(pcoa.centroids.se))
colnames(pcoa.cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
pcoa.cent.treats <- rownames(pcoa.cent.dataframe)

pcoa.col <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 2)) # Management
pcoa.shape <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 1))  # Plant

#Plot
df8a <- as.data.frame(pcoa.cent.dataframe)
plot8a <- ggplot(df8a, aes(x=V1, y=V2, colour=pcoa.col, shape = pcoa.shape,
                 group = interaction(pcoa.col, pcoa.shape))) + theme_bw() 
bact.2011<- plot8a + theme(panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(), 
               axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") + 
  geom_point(aes(fill=pcoa.col), colour = "black", size=6, stroke = 0.75) + 
  
  # Added By Mario ####
  geom_segment(data=fit.coords,aes(x=0,xend=Dim1,y=0,yend=Dim2), 
               arrow = arrow(length = unit(0.25, "cm")), 
               colour="grey20", linetype=4, inherit.aes = FALSE) + 
  geom_segment(data=fit.coords,aes(x=Dim1 * 0.98,xend=Dim1,y=Dim2 * 0.98,yend=Dim2), 
               arrow = arrow(length = unit(0.25, "cm")), 
               colour="grey20", inherit.aes = FALSE) +
  geom_text(data=fit.coords,aes(x=Dim1 * 1.125,y=Dim2 * 1.125, label=rownames(fit.coords)),
            size=3, inherit.aes = FALSE) +
  ####################


  scale_colour_manual(labels = c("Annual","Perennial"), 
                      values = c("#D55E00", "#0072B2")) + 
  scale_fill_manual(labels = c("Annual","Perennial"), 
                    values = c("#D55E00", "#0072B2")) + 
  scale_shape_manual(labels = c("HighN","LowN","Organic"),
                     values = c(21, 24, 22)) +
  #coord_cartesian(xlim = c(-0.25, 0.5), ylim = c(-0.35, 0.3)) + 
  theme(axis.title = element_text(size=18), axis.text=element_text(size=14), 
          axis.text.x = element_text(size=14), 
          panel.border = element_rect(colour = "black", size=1.25)) + 
  theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("PCoA 1 (35.7%)") + ylab("PCoA 2 (8.9%)") + 
  labs(fill = "Plant", shape = "Management") +
  guides(fill = guide_legend(override.aes = list(pch=21, size = 4, colour="black")),
         shape = guide_legend(override.aes = list(size = 4, fill="black"))) + 
         annotate("text", x = -0.12, y = 0.31, label = "bacteria-2011")

bact.2011

ggsave("../figures/bact.2011_PlantMgmt.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)

ggsave("../figures/bact.2011_PlantMgmt.png", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)

```

```{r Ordination (PCoA.2012) - Bacteria}
# PERMANOVA - 2012 only
new.data.2012 <- subset(new.data, Year == 2012)
adonis.2012 = adonis(new.data.2012[,-c(1:9)] ~Block+Management*Plant, method = "bray", data = new.data.2012, perm=1000)
adonis.2012

dataREL.dist <- vegdist(new.data.2012[,-c(1:9)], method="bray")

# Added by Mario ######
soil2012 <- soil[soil$Year == 2012, 17:22]
fit <- envfit(pcoa,soil2012,perm=1000)
fit
fit.coords <- as.data.frame(fit$vectors$arrows) * 0.1
############

pcoa <- cmdscale(dataREL.dist, k=3, eig=TRUE, add=FALSE)
  # Classical (Metric) Multidimensional Scaling; returns PCoA coordinates
  # eig=TRUE returns eigenvalues; k = # of dimensions to calculate

explainvar1b <- round(pcoa$eig[1] / sum(pcoa$eig), 3) * 100
explainvar2b <- round(pcoa$eig[2] / sum(pcoa$eig), 3) * 100
sum.eigb <- sum(explainvar1b, explainvar2b)

explainvar1b #28.9
explainvar2b #10.0

# Principal Coordinates Analysis (Mgmt*Plant) - 2012 only
pcoa.groups <- paste(new.data.2012$Management, new.data.2012$Plant, sep = "_")
pcoa.points <- data.frame(pcoa$points, group = pcoa.groups)

# Calculate Centroids (mean and SE)
pcoa.L.centroids <- melt(pcoa.points, id="group", measure.vars = c("X1", "X2"))
pcoa.centroids <- acast(pcoa.L.centroids, variable ~ group, mean)
pcoa.centroids.se <- acast(pcoa.L.centroids, variable ~ group, se)
pcoa.centroids.sd <- acast(pcoa.L.centroids, variable ~ group, sd)

# Combine
pcoa.cent.dataframe <- cbind(t(pcoa.centroids), t(pcoa.centroids.se))
colnames(pcoa.cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
pcoa.cent.treats <- rownames(pcoa.cent.dataframe)

pcoa.col <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 2)) # Management
pcoa.shape <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 1))  # Plant

#Plot
df9a <- as.data.frame(pcoa.cent.dataframe)
plot9a <- ggplot(df9a, aes(x=V1, y=V2, colour=pcoa.col, shape = pcoa.shape,
                 group = interaction(pcoa.col, pcoa.shape))) + theme_bw() 
bact.2012<- plot9a + theme(panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(), 
               axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") + 
  geom_point(aes(fill=pcoa.col), colour = "black", size=6, stroke = 0.75) + 
  
   # Added By Mario ####
  geom_segment(data=fit.coords,aes(x=0,xend=Dim1,y=0,yend=Dim2), 
               arrow = arrow(length = unit(0.25, "cm")), 
               colour="grey20", linetype=c(4,4,4,4,1), inherit.aes = FALSE) + 
  geom_segment(data=fit.coords,aes(x=Dim1 * 0.98,xend=Dim1,y=Dim2 * 0.98,yend=Dim2), 
               arrow = arrow(length = unit(0.25, "cm")), 
               colour="grey20", inherit.aes = FALSE) +
  geom_text(data=fit.coords,aes(x=Dim1 * 1.125,y=Dim2 * 1.125, label=rownames(fit.coords)),
            size=3, inherit.aes = FALSE) +
  ####################

  scale_colour_manual(labels = c("Annual","Perennial"), 
                      values = c("#D55E00", "#0072B2")) + 
  scale_fill_manual(labels = c("Annual","Perennial"), 
                    values = c("#D55E00", "#0072B2")) + 
  scale_shape_manual(labels = c("HighN","LowN","Organic"),
                     values = c(21, 24, 22)) +
  #coord_cartesian(xlim = c(-0.25, 0.5), ylim = c(-0.35, 0.3)) + 
  theme(axis.title = element_text(size=18), axis.text=element_text(size=14), 
          axis.text.x = element_text(size=14), 
          panel.border = element_rect(colour = "black", size=1.25)) + 
  theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("PCoA 1 (28.9%)") + ylab("PCoA 2 (10.0%)") + 
  labs(fill = "Plant", shape = "Management") +
  guides(fill = guide_legend(override.aes = list(pch=21, size = 4, colour="black")),
         shape = guide_legend(override.aes = list(size = 4, fill="black"))) + 
         annotate("text", x = -0.15, y = 0.31, label = "bacteria-2012")
bact.2012

ggsave("../figures/bact.2012_PlantMgmt.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)

ggsave("../figures/bact.2012_PlantMgmt.png", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)
```

```{r Ordination (PCoA.2013) - Bacteria}
# PERMANOVA - 2013 only
new.data.2013 <- subset(new.data, Year == 2013)
adonis.2013 = adonis(new.data.2013[,-c(1:9)] ~Block+Management*Plant, method = "bray", data = new.data.2013, perm=1000)
adonis.2013

dataREL.dist <- vegdist(new.data.2013[,-c(1:9)], method="bray")

# Added by Mario ######
soil2013 <- soil[soil$Year == 2013, 17:22]
fit <- envfit(pcoa,soil2013,perm=1000)
fit
fit.coords <- as.data.frame(fit$vectors$arrows) * 0.1
############

pcoa <- cmdscale(dataREL.dist, k=3, eig=TRUE, add=FALSE)
  # Classical (Metric) Multidimensional Scaling; returns PCoA coordinates
  # eig=TRUE returns eigenvalues; k = # of dimensions to calculate

explainvar1b <- round(pcoa$eig[1] / sum(pcoa$eig), 3) * 100
explainvar2b <- round(pcoa$eig[2] / sum(pcoa$eig), 3) * 100
sum.eigb <- sum(explainvar1b, explainvar2b)

explainvar1b #26.2
explainvar2b #13.8

# Principal Coordinates Analysis (Mgmt*Plant) - 2013 only
pcoa.groups <- paste(new.data.2013$Management, new.data.2013$Plant, sep = "_")
pcoa.points <- data.frame(pcoa$points, group = pcoa.groups)

# Calculate Centroids (mean and SE)
pcoa.L.centroids <- melt(pcoa.points, id="group", measure.vars = c("X1", "X2"))
pcoa.centroids <- acast(pcoa.L.centroids, variable ~ group, mean)
pcoa.centroids.se <- acast(pcoa.L.centroids, variable ~ group, se)
pcoa.centroids.sd <- acast(pcoa.L.centroids, variable ~ group, sd)

# Combine
pcoa.cent.dataframe <- cbind(t(pcoa.centroids), t(pcoa.centroids.se))
colnames(pcoa.cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
pcoa.cent.treats <- rownames(pcoa.cent.dataframe)

pcoa.col <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 2)) # Management
pcoa.shape <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 1))  # Plant

#Plot
df10a <- as.data.frame(pcoa.cent.dataframe)
plot10a <- ggplot(df10a, aes(x=V1, y=V2, colour=pcoa.col, shape = pcoa.shape,
                 group = interaction(pcoa.col, pcoa.shape))) + theme_bw() 
bact.2013<- plot10a + theme(panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(), 
               axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") + 
  geom_point(aes(fill=pcoa.col), colour = "black", size=6, stroke = 0.75) + 
  
     # Added By Mario ####
  geom_segment(data=fit.coords,aes(x=0,xend=Dim1,y=0,yend=Dim2), 
               arrow = arrow(length = unit(0.25, "cm")), 
               colour="grey20", linetype=c(4,4,4,1,1), inherit.aes = FALSE) + 
  geom_segment(data=fit.coords,aes(x=Dim1 * 0.98,xend=Dim1,y=Dim2 * 0.98,yend=Dim2), 
               arrow = arrow(length = unit(0.25, "cm")), 
               colour="grey20", inherit.aes = FALSE) +
  geom_text(data=fit.coords,aes(x=Dim1 * 1.125,y=Dim2 * 1.125, label=rownames(fit.coords)),
            size=3, inherit.aes = FALSE) +
  ####################

  scale_colour_manual(labels = c("Annual","Perennial"), 
                      values = c("#D55E00", "#0072B2")) + 
  scale_fill_manual(labels = c("Annual","Perennial"), 
                    values = c("#D55E00", "#0072B2")) + 
  scale_shape_manual(labels = c("HighN","LowN","Organic"),
                     values = c(21, 24, 22)) +
  #coord_cartesian(xlim = c(-0.25, 0.5), ylim = c(-0.35, 0.3)) + 
  theme(axis.title = element_text(size=18), axis.text=element_text(size=14), 
          axis.text.x = element_text(size=14), 
          panel.border = element_rect(colour = "black", size=1.25)) + 
  theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("PCoA 1 (26.2%)") + ylab("PCoA 2 (13.8%)") + 
  labs(fill = "Plant", shape = "Management") +
  guides(fill = guide_legend(override.aes = list(pch=21, size = 4, colour="black")),
         shape = guide_legend(override.aes = list(size = 4, fill="black"))) + 
         annotate("text", x = -0.1, y = 0.31, label = "bacteria-2013")

bact.2013

ggsave("../figures/bact.2013_PlantMgmt.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)

ggsave("../figures/bact.2013_PlantMgmt.png", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)
```

# Simple Hypothesis Testing - Nematodes
```{r perMANOVA - Nematodes}
#PERMANOVA Date|Plant|Management
str(nemaREL)
adonis2 = adonis(nemaREL[,-c(1:9)] ~Block+Date*Management*Plant, method = "bray", data = nemaREL, perm=1000)
adonis2
```
# Nematode Ordinations

## Principal Coordinates Ordination
```{r Ordination (PCoA) - Nematodes}
# Principal Coordinates Analysis - all years
dataREL.dist <- vegdist(dataRELnema, method="bray")

pcoa <- cmdscale(dataREL.dist, k=3, eig=TRUE, add=FALSE)
  # Classical (Metric) Multidimensional Scaling; returns PCoA coordinates
  # eig=TRUE returns eigenvalues; k = # of dimensions to calculate

explainvar1b <- round(pcoa$eig[1] / sum(pcoa$eig), 3) * 100
explainvar2b <- round(pcoa$eig[2] / sum(pcoa$eig), 3) * 100
sum.eigb <- sum(explainvar1b, explainvar2b)

explainvar1b #19.8
explainvar2b #18.3
```

```{r}
# Principal Coordinates Analysis Mgmt*Date
pcoa.groups <- paste(nemaREL$Management, nemaREL$Date, sep = "_")
pcoa.points <- data.frame(pcoa$points, group = pcoa.groups)

# Calculate Centroids (mean and SE)
pcoa.L.centroids <- melt(pcoa.points, id="group", measure.vars = c("X1", "X2"))
pcoa.centroids <- acast(pcoa.L.centroids, variable ~ group, mean)
pcoa.centroids.se <- acast(pcoa.L.centroids, variable ~ group, se)
pcoa.centroids.sd <- acast(pcoa.L.centroids, variable ~ group, sd)

# Combine
pcoa.cent.dataframe <- cbind(t(pcoa.centroids), t(pcoa.centroids.se))
colnames(pcoa.cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
pcoa.cent.treats <- rownames(pcoa.cent.dataframe)

pcoa.col <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 2)) # Management
pcoa.shape <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 1))  # Date

# Principal Coordinates Analysis (Mgmt*Date)
df3a <- as.data.frame(pcoa.cent.dataframe)
plot3a <- ggplot(df3a, aes(x=V1, y=V2, colour=pcoa.col, shape = pcoa.shape,
                 group = interaction(pcoa.col, pcoa.shape))) + theme_bw() 
plot3a + theme(panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(), 
               axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") + 
  geom_point(aes(fill=pcoa.col), colour = "black", size=6, stroke = 0.75) + 
  scale_colour_manual(labels = c("2011","2012", "2013"), 
                      values = c("#FFFFFF", "#FFFF00","#336600")) + 
  scale_fill_manual(labels = c("2011","2012", "2013"), 
                    values = c("#FFFFFF", "#FFFF00","#336600"))  + 
  scale_shape_manual(labels = c("HighN","LowN","Organic"),
                     values = c(21, 24, 22)) +
  #coord_cartesian(xlim = c(-0.25, 0.5), ylim = c(-0.35, 0.3)) + 
  theme(axis.title = element_text(size=18), axis.text=element_text(size=14), 
          axis.text.x = element_text(size=14), 
          panel.border = element_rect(colour = "black", size=1.25)) + 
  theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("PCoA 1 (19.8%)") + ylab("PCoA 2 (18.3%)") + 
  labs(fill = "Date", shape = "Management") +
  guides(fill = guide_legend(override.aes = list(pch=21, size = 4, colour="black")),
         shape = guide_legend(override.aes = list(size = 4, fill="black"))) + 
         annotate("text", x = -0.12, y = 0.14, label = "nematodes")

ggsave("../figures/nema_PWES_YrMgmt.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)

```

```{r}
# Principal Coordinates Analysis (Mgmt*Plant)
pcoa.groups <- paste(nemaREL$Management, nemaREL$Plant, sep = "_")
pcoa.points <- data.frame(pcoa$points, group = pcoa.groups)

# Calculate Centroids (mean and SE)
pcoa.L.centroids <- melt(pcoa.points, id="group", measure.vars = c("X1", "X2"))
pcoa.centroids <- acast(pcoa.L.centroids, variable ~ group, mean)
pcoa.centroids.se <- acast(pcoa.L.centroids, variable ~ group, se)
pcoa.centroids.sd <- acast(pcoa.L.centroids, variable ~ group, sd)

# Combine
pcoa.cent.dataframe <- cbind(t(pcoa.centroids), t(pcoa.centroids.se))
colnames(pcoa.cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
pcoa.cent.treats <- rownames(pcoa.cent.dataframe)

pcoa.col <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 2)) # Management
pcoa.shape <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 1))  # Plant

#Plot
df4a <- as.data.frame(pcoa.cent.dataframe)
plot4a <- ggplot(df4a, aes(x=V1, y=V2, colour=pcoa.col, shape = pcoa.shape,
                 group = interaction(pcoa.col, pcoa.shape))) + theme_bw() 
plot4a + theme(panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(), 
               axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") + 
  geom_point(aes(fill=pcoa.col), colour = "black", size=6, stroke = 0.75) + 
  scale_colour_manual(labels = c("Annual","Perennial"), 
                      values = c("#D55E00", "#0072B2")) + 
  scale_fill_manual(labels = c("Annual","Perennial"), 
                    values = c("#D55E00", "#0072B2")) + 
  scale_shape_manual(labels = c("HighN","LowN","Organic"),
                     values = c(21, 24, 22)) +
  #coord_cartesian(xlim = c(-0.25, 0.5), ylim = c(-0.35, 0.3)) + 
  theme(axis.title = element_text(size=18), axis.text=element_text(size=14), 
          axis.text.x = element_text(size=14), 
          panel.border = element_rect(colour = "black", size=1.25)) + 
  theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("PCoA 1 (19.8%)") + ylab("PCoA 2 (18.3%)") + 
  labs(fill = "Plant", shape = "Management") +
  guides(fill = guide_legend(override.aes = list(pch=21, size = 4, colour="black")),
         shape = guide_legend(override.aes = list(size = 4, fill="black"))) + 
         annotate("text", x = -0.14, y = 0.2, label = "nematodes")

ggsave("../figures/nema_PlantMgmt.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)
```

## Principal Coordinates Ordination - NEMATODES seaparate years
```{r Ordination (PCoA.2011) - Nematodes}
nemaREL.2011 <- subset(nemaREL, Year == 2011)
dim(nemaREL)
dim(nemaREL.2011)

# PERMANOVA - 2011 only
adonis(nemaREL.2011[,-c(1:9)]~Block+Management*Plant, data=nemaREL.2011)

dataREL.dist <- vegdist(nemaREL.2011[,-c(1:9)], method="bray")

pcoa <- cmdscale(dataREL.dist, k=3, eig=TRUE, add=FALSE)
  # Classical (Metric) Multidimensional Scaling; returns PCoA coordinates
  # eig=TRUE returns eigenvalues; k = # of dimensions to calculate

explainvar1b <- round(pcoa$eig[1] / sum(pcoa$eig), 3) * 100
explainvar2b <- round(pcoa$eig[2] / sum(pcoa$eig), 3) * 100
sum.eigb <- sum(explainvar1b, explainvar2b)

explainvar1b #28.6
explainvar2b #22.0

# Principal Coordinates Analysis (Mgmt*Plant) - 2011 only
pcoa.groups <- paste(nemaREL.2011$Management, nemaREL.2011$Plant, sep = "_")
pcoa.points <- data.frame(pcoa$points, group = pcoa.groups)

# Calculate Centroids (mean and SE)
pcoa.L.centroids <- melt(pcoa.points, id="group", measure.vars = c("X1", "X2"))
pcoa.centroids <- acast(pcoa.L.centroids, variable ~ group, mean)
pcoa.centroids.se <- acast(pcoa.L.centroids, variable ~ group, se)
pcoa.centroids.sd <- acast(pcoa.L.centroids, variable ~ group, sd)

# Combine
pcoa.cent.dataframe <- cbind(t(pcoa.centroids), t(pcoa.centroids.se))
colnames(pcoa.cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
pcoa.cent.treats <- rownames(pcoa.cent.dataframe)

pcoa.col <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 2)) # Management
pcoa.shape <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 1))  # Plant

#Plot
df7a <- as.data.frame(pcoa.cent.dataframe)
plot7a <- ggplot(df7a, aes(x=V1, y=V2, colour=pcoa.col, shape = pcoa.shape,
                 group = interaction(pcoa.col, pcoa.shape))) + theme_bw() 
nema.2011<- plot7a + theme(panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(), 
               axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") + 
  geom_point(aes(fill=pcoa.col), colour = "black", size=6, stroke = 0.75) + 
  scale_colour_manual(labels = c("Annual","Perennial"), 
                      values = c("#D55E00", "#0072B2")) + 
  scale_fill_manual(labels = c("Annual","Perennial"), 
                    values = c("#D55E00", "#0072B2")) + 
  scale_shape_manual(labels = c("HighN","LowN","Organic"),
                     values = c(21, 24, 22)) +
  #coord_cartesian(xlim = c(-0.25, 0.5), ylim = c(-0.35, 0.3)) + 
  theme(axis.title = element_text(size=18), axis.text=element_text(size=14), 
          axis.text.x = element_text(size=14), 
          panel.border = element_rect(colour = "black", size=1.25)) + 
  theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("PCoA 1 (28.6%)") + ylab("PCoA 2 (22.0%)") + 
  labs(fill = "Plant", shape = "Management") +
  guides(fill = guide_legend(override.aes = list(pch=21, size = 4, colour="black")),
         shape = guide_legend(override.aes = list(size = 4, fill="black"))) + 
         annotate("text", x = -0.15, y = 0.31, label = "nematodes-2011")

ggsave("../figures/nema.2011_PlantMgmt.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)

ggsave("../figures/nema.2011_PlantMgmt.png", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)
```

```{r Ordination (PCoA.2012) - Nematodes}

nemaREL.2012 <- subset(nemaREL, Year == 2012)
dim(nemaREL)
dim(nemaREL.2012)

# PERMANOVA  - 2012 only
adonis(nemaREL.2012[,-c(1:9)]~Block+Management*Plant, data=nemaREL.2012)

dataREL.dist <- vegdist(nemaREL.2012[,-c(1:9)], method="bray")

pcoa <- cmdscale(dataREL.dist, k=3, eig=TRUE, add=FALSE)
  # Classical (Metric) Multidimensional Scaling; returns PCoA coordinates
  # eig=TRUE returns eigenvalues; k = # of dimensions to calculate

explainvar1b <- round(pcoa$eig[1] / sum(pcoa$eig), 3) * 100
explainvar2b <- round(pcoa$eig[2] / sum(pcoa$eig), 3) * 100
sum.eigb <- sum(explainvar1b, explainvar2b)

explainvar1b #25.8
explainvar2b #17.6

# Principal Coordinates Analysis (Mgmt*Plant) - 2012 only
pcoa.groups <- paste(nemaREL.2012$Management, nemaREL.2012$Plant, sep = "_")
pcoa.points <- data.frame(pcoa$points, group = pcoa.groups)

# Calculate Centroids (mean and SE)
pcoa.L.centroids <- melt(pcoa.points, id="group", measure.vars = c("X1", "X2"))
pcoa.centroids <- acast(pcoa.L.centroids, variable ~ group, mean)
pcoa.centroids.se <- acast(pcoa.L.centroids, variable ~ group, se)
pcoa.centroids.sd <- acast(pcoa.L.centroids, variable ~ group, sd)

# Combine
pcoa.cent.dataframe <- cbind(t(pcoa.centroids), t(pcoa.centroids.se))
colnames(pcoa.cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
pcoa.cent.treats <- rownames(pcoa.cent.dataframe)

pcoa.col <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 2)) # Management
pcoa.shape <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 1))  # Plant

#Plot
df6a <- as.data.frame(pcoa.cent.dataframe)
plot6a <- ggplot(df6a, aes(x=V1, y=V2, colour=pcoa.col, shape = pcoa.shape,
                 group = interaction(pcoa.col, pcoa.shape))) + theme_bw() 
nema.2012<- plot6a + theme(panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(), 
               axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") + 
  geom_point(aes(fill=pcoa.col), colour = "black", size=6, stroke = 0.75) + 
  scale_colour_manual(labels = c("Annual","Perennial"), 
                      values = c("#D55E00", "#0072B2")) + 
  scale_fill_manual(labels = c("Annual","Perennial"), 
                    values = c("#D55E00", "#0072B2")) + 
  scale_shape_manual(labels = c("HighN","LowN","Organic"),
                     values = c(21, 24, 22)) +
  #coord_cartesian(xlim = c(-0.25, 0.5), ylim = c(-0.35, 0.3)) + 
  theme(axis.title = element_text(size=18), axis.text=element_text(size=14), 
          axis.text.x = element_text(size=14), 
          panel.border = element_rect(colour = "black", size=1.25)) + 
  theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("PCoA 1 (25.8%)") + ylab("PCoA 2 (17.6%)") + 
  labs(fill = "Plant", shape = "Management") +
  guides(fill = guide_legend(override.aes = list(pch=21, size = 4, colour="black")),
         shape = guide_legend(override.aes = list(size = 4, fill="black"))) + 
         annotate("text", x = -0.15, y = 0.31, label = "nematodes-2012")

ggsave("../figures/nema.2012_PlantMgmt.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)

ggsave("../figures/nema.2012_PlantMgmt.png", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)
```

```{r Ordination (PCoA.2013) - Nematodes}
nemaREL.2013 <- subset(nemaREL, Year == 2013)

# PERMANOVA  - 2013 only
adonis(nemaREL.2013[,-c(1:9)]~Block+Management*Plant, data=nemaREL.2013)

dataREL.dist <- vegdist(nemaREL.2013[,-c(1:9)], method="bray")

pcoa <- cmdscale(dataREL.dist, k=3, eig=TRUE, add=FALSE)
  # Classical (Metric) Multidimensional Scaling; returns PCoA coordinates
  # eig=TRUE returns eigenvalues; k = # of dimensions to calculate

explainvar1b <- round(pcoa$eig[1] / sum(pcoa$eig), 3) * 100
explainvar2b <- round(pcoa$eig[2] / sum(pcoa$eig), 3) * 100
sum.eigb <- sum(explainvar1b, explainvar2b)

explainvar1b #27.0
explainvar2b #24.2

# Principal Coordinates Analysis (Mgmt*Plant) - 2013 only
pcoa.groups <- paste(nemaREL.2013$Management, nemaREL.2013$Plant, sep = "_")
pcoa.points <- data.frame(pcoa$points, group = pcoa.groups)

# Calculate Centroids (mean and SE)
pcoa.L.centroids <- melt(pcoa.points, id="group", measure.vars = c("X1", "X2"))
pcoa.centroids <- acast(pcoa.L.centroids, variable ~ group, mean)
pcoa.centroids.se <- acast(pcoa.L.centroids, variable ~ group, se)
pcoa.centroids.sd <- acast(pcoa.L.centroids, variable ~ group, sd)

# Combine
pcoa.cent.dataframe <- cbind(t(pcoa.centroids), t(pcoa.centroids.se))
colnames(pcoa.cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
pcoa.cent.treats <- rownames(pcoa.cent.dataframe)

pcoa.col <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 2)) # Management
pcoa.shape <- as.factor(sapply(strsplit(pcoa.cent.treats, "_"), `[`, 1))  # Plant

#Plot
df5a <- as.data.frame(pcoa.cent.dataframe)
plot5a <- ggplot(df5a, aes(x=V1, y=V2, colour=pcoa.col, shape = pcoa.shape,
                 group = interaction(pcoa.col, pcoa.shape))) + theme_bw() 
nema.2013<- plot5a + theme(panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(), 
               axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") + 
  geom_point(aes(fill=pcoa.col), colour = "black", size=6, stroke = 0.75) + 
  scale_colour_manual(labels = c("Annual","Perennial"), 
                      values = c("#D55E00", "#0072B2")) + 
  scale_fill_manual(labels = c("Annual","Perennial"), 
                    values = c("#D55E00", "#0072B2")) + 
  scale_shape_manual(labels = c("HighN","LowN","Organic"),
                     values = c(21, 24, 22)) +
  #coord_cartesian(xlim = c(-0.25, 0.5), ylim = c(-0.35, 0.3)) + 
  theme(axis.title = element_text(size=18), axis.text=element_text(size=14), 
          axis.text.x = element_text(size=14), 
          panel.border = element_rect(colour = "black", size=1.25)) + 
  theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("PCoA 1 (27.0%)") + ylab("PCoA 2 (24.2%)") + 
  labs(fill = "Plant", shape = "Management") +
  guides(fill = guide_legend(override.aes = list(pch=21, size = 4, colour="black")),
         shape = guide_legend(override.aes = list(size = 4, fill="black"))) + 
         annotate("text", x = -0.1, y = 0.31, label = "nematodes-2013")

ggsave("../figures/nema.2013_PlantMgmt.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)

ggsave("../figures/nema.2013_PlantMgmt.png", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=900, limitsize=TRUE)
```
# Bacterial community indicator species analysis 2013 only - plant
```{r}
new.data <-cbind(design,dataREL)
library("labdsv")

new.data.2013 <- subset(new.data, Year == 2013)
design.type <- new.data.2013$Plant
dataREL.2013 <- new.data.2013[,-c(1:9)]

dataREL <- dataREL.2013[, colSums(dataREL.2013) > 0.05]
bac.ind <- indval(dataREL, design.type)
levels(design.type)
summary(bac.ind)

inds <- which(bac.ind$pval <= 0.05)
bac.indicators <- as.data.frame(matrix(NA, nrow = length(inds), ncol = 4))
colnames(bac.indicators) <- c("OTU", "Cluster", "IndVal", "Prob")

bac.indicators$OTU <- names(inds)
bac.indicators$Cluster <- bac.ind$maxcls[inds]
bac.indicators$IndVal <- bac.ind$indcls[inds]
bac.indicators$Prob <- bac.ind$pval[inds]

ind.tax <- otu.tax[which(as.character(otu.tax$OTU) %in% bac.indicators$OTU), ]
ind.tax <- ind.tax[match(ind.tax$OTU, bac.indicators$OTU), ]

indicator.bac <- cbind(bac.indicators, ind.tax[, -c(1)])

indicator.bac <- indicator.bac[order(as.numeric(indicator.bac$Cluster)), ]

table(indicator.bac$Cluster)
table(indicator.bac$Phylum)
table(indicator.bac$Cluster)
levels(design.type)

# Export Bacteria Indicator Table
write.table(indicator.bac, "../data/BacterialIndicators_Plant.txt",
            sep="\t", row.names = F, quote = F)

#bac.ind - by management
design.type <- design$Management

dataREL <- dataREL.2013[, colSums(dataREL.2013) > 0.05]
bac.ind <- indval(dataREL, design.type)
levels(design.type)
summary(bac.ind)

inds <- which(bac.ind$pval <= 0.05)
bac.indicators <- as.data.frame(matrix(NA, nrow = length(inds), ncol = 4))
colnames(bac.indicators) <- c("OTU", "Cluster", "IndVal", "Prob")

bac.indicators$OTU <- names(inds)
bac.indicators$Cluster <- bac.ind$maxcls[inds]
bac.indicators$IndVal <- bac.ind$indcls[inds]
bac.indicators$Prob <- bac.ind$pval[inds]

ind.tax <- otu.tax[which(as.character(otu.tax$OTU) %in% bac.indicators$OTU), ]
ind.tax <- ind.tax[match(ind.tax$OTU, bac.indicators$OTU), ]

indicator.bac <- cbind(bac.indicators, ind.tax[, -c(1)])

indicator.bac <- indicator.bac[order(as.numeric(indicator.bac$Cluster)), ]

table(indicator.bac$Cluster)
table(indicator.bac$Phylum)
table(indicator.bac$Cluster)
levels(design.type)

# Export Bacteria Indicator Table
write.table(indicator.bac, "../data/BacterialIndicators_Mgmt.txt",
            sep="\t", row.names = F, quote = F)
```
# Nematode community indicator species analysis 2013 only - plant and mgmt
```{r}
nemaREL <- cbind(nema.design,dataRELnema)
library("labdsv")

new.data.2013 <- subset(nemaREL, Year == 2013)
design.type <- new.data.2013$Plant
dataREL.2013 <- new.data.2013[,-c(1:9)]

dataREL <- dataREL.2013[, colSums(dataREL.2013) > 0.05]
nema.ind <- indval(dataREL, design.type)
levels(design.type)
summary(nema.ind)

inds <- which(nema.ind$pval <= 0.05)
nema.indicators <- as.data.frame(matrix(NA, nrow = length(inds), ncol = 4))
colnames(nema.indicators) <- c("taxa", "Cluster", "IndVal", "Prob")

nema.indicators$taxa <- names(inds)
nema.indicators$Cluster <- nema.ind$maxcls[inds]
nema.indicators$IndVal <- nema.ind$indcls[inds]
nema.indicators$Prob <- nema.ind$pval[inds]

#ind.tax <- otu.tax[which(as.character(otu.tax$OTU) %in% bac.indicators$OTU), ]
#ind.tax <- ind.tax[match(ind.tax$OTU, bac.indicators$OTU), ]
#indicator.bac <- cbind(bac.indicators, ind.tax[, -c(1)])

indicators <- nema.indicators[order(as.numeric(nema.indicators$Cluster)), ]

table(indicators$Cluster)
table(indicators$taxa)
table(indicators$Cluster)
levels(design.type)

# Export Nematod Indicator Table
write.table(indicators, "../data/NemaIndicators_Plant.txt",
            sep="\t", row.names = F, quote = F)

#nema.ind - by management
design.type <- new.data.2013$Management
dataREL.2013 <- new.data.2013[,-c(1:9)]

dataREL <- dataREL.2013[, colSums(dataREL.2013) > 0.05]
nema.ind <- indval(dataREL, design.type)
levels(design.type)
summary(nema.ind)

inds <- which(nema.ind$pval <= 0.05)
nema.indicators <- as.data.frame(matrix(NA, nrow = length(inds), ncol = 4))
colnames(nema.indicators) <- c("taxa", "Cluster", "IndVal", "Prob")

nema.indicators$taxa <- names(inds)
nema.indicators$Cluster <- nema.ind$maxcls[inds]
nema.indicators$IndVal <- nema.ind$indcls[inds]
nema.indicators$Prob <- nema.ind$pval[inds]

indicators <- nema.indicators[order(as.numeric(nema.indicators$Cluster)), ]

table(indicators$Cluster)
table(indicators$taxa)
table(indicators$Cluster)
levels(design.type)

# Export Nematod Indicator Table
write.table(indicators, "../data/NemaIndicators_Plant.txt",
            sep="\t", row.names = F, quote = F)
```
